\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-07-05 paper/paper.tex

% math macros 
\newcommand{\ind}{\stackrel{ind.}{\sim}}
\newcommand{\op}{\operatorname}

@@

Failure distributions of high-reliability consumer products can be difficult
to assess; when field data are available, information may be limited. In this paper, we propose the use of Bayesian hierarchical modeling to borrow
information, improving inferences on lifetime
distributions where information is limited by right-censoring and
left-truncation.

The reliability of many engineered products follow a similar pattern. Relatively high rates of failure occur in early life ("infant mortality"). This can often be explained by defects from the manufacturing process. Following a period of "burn-in", after which the majority of the defective units have failed, failure rates flatten out during a period. Finally, after prolonged use, rates of failure increase due to wearout.  Ignoring this pattern in failure rates can lead to suboptimal decisions. While simple nonparametric methods are available, these are not suitable for forecasting.

@@

>>>>

% math macros

\newcommand{\ind}{\stackrel{ind.}{\sim}}
\newcommand{\op}{\operatorname}

@@

Failure distributions of high-reliability consumer products can be difficult to assess.  Even when field data are available, information may be limited for a variety of reasons.  Certain brands may have few products in operation resulting in small sample sizes.  Other products may have many observed units in operation but few observed failures or limited time under observation, which makes fitting a parametric lifetime model problematic.  In this paper, we propose the use of Bayesian hierarchical modeling to borrow information across products, thereby improving inferences on lifetime distributions where information is limited by small sample sizes, left-truncation, and right censoring.

The reliability of many engineered products follow a similar pattern. Relatively high rates of failure occurring in early life ("infant mortality") due to defects from the manufacturing process. Following a period of "burn-in", after which the majority of the defective units have failed, failure rates flatten out during a period. Finally, after prolonged use, rates of failure increase due to wearout.  Ignoring this pattern in failure rates can lead to suboptimal decisions and spurious inferences about a product's reliability.   While simple nonparametric methods are available, such as the Kaplan-Meier estimator, these are not suitable for forecasting.  They also do not allow for a straight forward statistical comparisons of different brands in order to select the most reliable product.

@@

To model this mixture of failure distributions in a unified framework, Chan and Meeker proposed the Generalized Limited Failure Population (GLFP) model \citet{chan}.  In addition to describing the failure time distribution for products that are susceptible to infant mortality and wearout failure modes, it theorizes an unknown proportion of defective units which are susceptible to defects.    While the GLFP model provides flexibility over a simple or piece-wise parametric model, it can be difficult to fit with limited data  As Chan and Meeker discuss in their original paper, few observed failures in addition to unknown causes of failure cause maximum likelihood estimates to be unstable or impossible to obtain.  Therefore, when multiple populations are of interest, comparisons based on the standard GLFP model are restricted to those with sufficient data and observed failure from each failure mode.  A naive approach to this limitation is to combine the data from all products and fit a single GLFP model.  This model can be well-estimated, but the pooled GLFP model fits poorly.  At the other extreme, fitting a separate GLFP model to each product is problematic for products where the data are weakly informative.  Due to identifiability issues, in these cases the model fit is unstable unless strongly informative priors are placed on the model parameters.  \\

We therefore propose to fit the GLFP model using a hierarchical Bayesian approach.  A hierarchical model is advantageous as allows for borrowing of information to improve estimation of the GLFP parameters for a whole class of products.  Moreover, the hierarchical model is a nice compromise between the aggregate and individual modeling approaches: product brands with lots of failures are estimated precisely; and in cases where little data is available the hierarchical model borrows information from other products to obtain stable estimates.  This allows us to include all of the data and more importantly, make valid inferences for each individual product.

In the case of complex, high-reliability systems where cause of failure is
not available, a model which
\begin{enumerate}[a.]
\item has parameters that can be estimated from the observed data
\item is flexible enough to fit the observed data
\item in interpretable with respect to available theory of the underlying process
\end{enumerate}
is desired. We present a Bayesian, hierarchical modeling approach for
grouped failure data. As a benefit of working with Monte Carlo
samples, we can easily make inference on a wide range of quantities of
interest while accounting for uncertainty. We demonstrate this approach on real data hard
drive failure data from a
cloud-based storage company.
